Copy number inference with InferCNV

### 2024-05-20 analyses/cell-type-ewings/exploratory_analysis/04-infercnv.Rmd
don't create null pngs

# png ref files 
png_files <- all_results_dir_list |>
  purrr::map_chr(\(dir) file.path(dir, glue::glue("{params$library_id}_infercnv.png"))) |> 
  # make sure png files exists
  purrr::map(\(file)
    stopifnot("Missing PNG file" = file.exists(file))
  )

>>>>

# png ref files 
png_files <- all_results_dir_list |>
  purrr::map_chr(\(dir) file.path(dir, glue::glue("{params$library_id}_infercnv.png")))

png_files |> 
  # make sure png files exists
  purrr::map(\(file)
    stopifnot("Missing PNG file" = file.exists(file))
  )
